Supplement

### 2023-07-31 paper/manuscript.Rmd
tweaks
final clarifications!

Many predictors correlated with subjective replication success using unadjusted Pearson correlations(Table \ref{tab:cor}). Predictors of higher replicability included within-participants designs, larger numbers of trials per participant, and the original study having openly accessible data. Predictors of lower replicability included single-vignette studies (those with only one experimental stimulus per condition), classification as social psychology, and study pairs where the original study was in-person and the replication switched to online.

@@

While a number of features show individual correlations with the subjective replication score, many correlate with one another. To determine which predictors were the strongest, we ran a series of pre-registered Bayesian regression models using an ordinal link function and  regularized using a horseshoe shrinkage prior [@carvalho09]. We first ran models using all of the original-replication pairs (N=176), but without original effect size and original $p$ value as predictors, as they were uncodable for some pairs. We next ran models including all predictors, but on only the subset of data where all predictors were available (N=112).

@@

```{r mod-results, out.width="90%", fig.width=8, fig.height=5, fig.pos="ht", fig.cap="Odds ratios and corresponding uncertaintly estimates on the likelihood of having a higher subjective replication score as a function of the dependent variable. Estimates from a model of all original-replication pairs (N=176) are shown in blue, and from a model of all pairs with full statistical information (N=112) are shown in red. A value of 1 indicates no effect, greater than one indicates an association with higher replication scores and less than 1 an association with lower replication scores."}

@@

We are grateful to the students in PSYCH 254 and PSYCH 251 for conducting the replication projects included here. We thank Ben Prystawski and the FriSem audience for feedback on earlier versions of this work. TODO GRANTS??

@@

The authors have no conflicts of interest to declare. TODO contributor statement!
# References {-}

>>>>

Many predictors correlated with subjective replication success using unadjusted Pearson correlations (Table \ref{tab:cor}). Predictors of higher replicability included within-participants designs, larger numbers of trials per participant, and the original study having openly accessible data. Predictors of lower replicability included single-vignette studies (those with only one experimental stimulus per condition), classification as social psychology, and study pairs where the original study was in-person and the replication switched to online.

@@

While a number of features show individual correlations with the subjective replication score, many correlate with one another. To determine which predictors were the strongest, we modeled subjective replication score as an ordinal outcome using ordinal Bayesian regression models with a logit link function, regularized using a horseshoe shrinkage prior [@carvalho09]. This model estimates odds ratios representing the association of the predictor with having a higher versus lower subjective replication score. We first ran models using all of the original-replication pairs (N=176), but without original effect size and original $p$ value as predictors, as they were uncodable for some pairs. We next ran models including all predictors, but on only the subset of data where all predictors were available (N=112).

@@

```{r mod-results, out.width="90%", fig.width=8, fig.height=5, fig.pos="ht", fig.cap="Odds ratios and corresponding 95\\% CrI on the likelihood of having a higher subjective replication score as a function of the independent variable. Estimates from a model of all original-replication pairs (N=176) are shown in blue, and from a model of all pairs with full statistical information (N=112) are shown in red. A value of 1 indicates no association, greater than one indicates an association with higher replication scores and less than 1 an association with lower replication scores."}

@@

We are grateful to the students in PSYCH 254 and PSYCH 251 for conducting the replication projects included here. We thank Ben Prystawski and the FriSem audience for feedback on earlier versions of this work. MM was supported by R01LM013866.

@@

VB and MCF report no conflicts of interest. MM is the Associate Director of the Stanford Center for Open and Reproducible Science.

The authors made the following contributions: VB: Methodology, Data Curation, Formal Analysis, Writing - original draft; 
MM:  Methodology, Writing - review & editing; 
MCF: Conceptualization, Methodology, Writing - review & editing.

# References {-}

### 2023-07-31 paper/manuscript.tex
tweaks
final clarifications!

While a number of features show individual correlations with the subjective replication score, many correlate with one another. To determine which predictors were the strongest, we ran a series of pre-registered Bayesian regression models using an ordinal link function and regularized using a horseshoe shrinkage prior (\protect\hyperlink{ref-carvalho09}{Carvalho et al. 2009}). We first ran models using all of the original-replication pairs (N=176), but without original effect size and original \(p\) value as predictors, as they were uncodable for some pairs. We next ran models including all predictors, but on only the subset of data where all predictors were available (N=112).

@@

\begin{figure}[ht]
\includegraphics[width=0.9\linewidth]{manuscript_files/figure-latex/mod-results-1} \caption{Odds ratios and corresponding uncertaintly estimates on the likelihood of having a higher subjective replication score as a function of the dependent variable. Estimates from a model of all original-replication pairs (N=176) are shown in blue, and from a model of all pairs with full statistical information (N=112) are shown in red. A value of 1 indicates no effect, greater than one indicates an association with higher replication scores and less than 1 an association with lower replication scores.}\label{fig:mod-results}
\end{figure}

@@

The authors have no conflicts of interest to declare. TODO contributor statement!
\# References \{-\}

>>>>

While a number of features show individual correlations with the subjective replication score, many correlate with one another. To determine which predictors were the strongest, we modeled subjective replication score as an ordinal outcome using ordinal Bayesian regression models with a logit link function, regularized using a horseshoe shrinkage prior (\protect\hyperlink{ref-carvalho09}{Carvalho et al. 2009}). This model estimates odds ratios representing the association of the predictor with having a higher versus lower subjective replication score. We first ran models using all of the original-replication pairs (N=176), but without original effect size and original \(p\) value as predictors, as they were uncodable for some pairs. We next ran models including all predictors, but on only the subset of data where all predictors were available (N=112).

@@

\begin{figure}[ht]
\includegraphics[width=0.9\linewidth]{manuscript_files/figure-latex/mod-results-1} \caption{Odds ratios and corresponding 95\% CrI on the likelihood of having a higher subjective replication score as a function of the independent variable. Estimates from a model of all original-replication pairs (N=176) are shown in blue, and from a model of all pairs with full statistical information (N=112) are shown in red. A value of 1 indicates no association, greater than one indicates an association with higher replication scores and less than 1 an association with lower replication scores.}\label{fig:mod-results}
\end{figure}

@@

VB and MCF report no conflicts of interest. MM is the Associate Director of the Stanford Center for Open and Reproducible Science.

The authors made the following contributions: VB: Methodology, Data Curation, Formal Analysis, Writing - original draft;
MM: Methodology, Writing - review \& editing;
MCF: Conceptualization, Methodology, Writing - review \& editing.

\hypertarget{references}{%
\section*{References}\label{references}}
\addcontentsline{toc}{section}{References}

### 2023-07-31 paper/supplement.Rmd
final clarifications!

As a check on whether our results were sensitive to the inclusion of pairs that were marginal in some way, we repeated the 6 models including only studies that were not marginal.

>>>>

As a check on whether our results were sensitive to the inclusion of pairs that were marginal in some way, we repeated the 6 models including only studies that were not marginal. For sensitivity analyses, we completely excluded some studies where the replication analysis was not the focal analysis of the original (ex. student chose a manipulation check as their primary analysis). We also excluded studies with extremely small or lop-sided sample sizes.

For some studies that were included with some statistical outcomes in the main results, we downgraded them to experimental features only for sensitivity. Here, we felt the replication itself didn't have major problems and we felt confident in the subjective replication score reflecting holistically on the replication. However, there were some mismatches in the statistical reporting that meant we were not confident enough if your numeric calculations for the paper. Common mismatches were  where one reported a t-test and the other reported mean and SDs, and when degrees of freedom seemed inconsistent across replication and original (suggesting different groupings or levels of analysis).
